Developmental trajectories of word recognition: a priming study in bilinguals

### 2023-10-27 manuscript/manuscript.qmd
Simplify analysis, only one model with two contrasts

The formation of a mental lexicon is a critical developmental achievement for infants_ learning words allows infants to retrieve socially relevant concepts from fairly arbitrary linguistic forms embedded in speech.

Learning words allows infants to access the rich world made of concepts through the recognition of fairly arbitrary linguistic forms, i.e., words. This remarkable developmental achievement is

There is evidence of cascaded activation during lexical access.

@chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors. In each trial, the authors presented participants with four semantically and phonologically pictures. Four seconds after pictures onset, a word-form was auditorily presented. The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category. For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress. Then they would hear the carrier phrase "Look at the **bee**!". The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial. These results support a cascaded activation account of lexical access during the first stages of lexical development.

@@

How does language co-activation shape lexical development?
Marian and Spivey (1999)
Costa et al. (2000)

@@

@@

@@

```{r fig-ptlt-descriptive}
#| label: fig-ptlt-descriptive
#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
data_time_related |> 
	summarise(.elog = mean(.elog),
			  .by = c(session_id, timebin, lp, condition)) |> 
	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
	facet_wrap(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 width = 0.5) +
	stat_summary(fun = mean,
				 geom = "line") +
	stat_summary(fun = mean,
				 geom = "point") +
	theme(axis.title.x = element_blank()) +

	data_time_cognate |> 
	summarise(.elog = mean(.elog),
			  .by = c(session_id, timebin, lp, condition)) |> 
	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
	facet_wrap(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 width = 0.5) +
	stat_summary(fun = mean,
				 geom = "line") +
	stat_summary(fun = mean,
				 geom = "point") +
	theme(strip.text = element_blank()) +

@@

### Phonological priming: Related vs. Unrelated primes

@@

```{r fig-related-aggregated}
#| label: fig-related-aggregated
#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials. Each point represents the mean probability of target looking for one participant in one testing session. Lines link observations from the same testing session across conditions. Black dots and errorbars indicate the mean and 95% CrI. B) Aggregated probability of target looking across ages for related and unrelated trials. Lines and error bands indicate the mean and standard error of the mean."
nd <- expand(data_related, lp, condition, age = mean(data_related$age))

epreds <- add_epred_draws(newdata = nd,
						  object = model_fits_related[[1]],
						  re_formula = NA) |> 
	mean_qi() |> 
	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))

epreds |> 
	ggplot(aes(condition, .epred, 
			   colour = condition,
			   fill = condition)) +
	facet_wrap(~lp) +
	# geom_line(data = data_related,
	# 		  aes(y = .elog,
	# 		  	group = session_id),
	# 		  colour = "grey",
	# 		  alpha = 1/4) +
	geom_dots(dat = data_related,
			  aes(y = .elog,
			  	side = ifelse(condition=="Related",
			  				  "left", 
			  				  "right")),
			  show.legend = FALSE) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	geom_line(aes(group = lp),
			  colour = "black",
			  linewidth = 3/4) +
	geom_errorbar(aes(ymin = .lower,
					  ymax = .upper),
				  width = 0.15,
				  linewidth = 3/4,
				  colour = "black") +
	geom_point(size = 2, colour = "black") +
	geom_label(aes(label = label,
				   y = -1.5),
			   fill = "white",
			   colour = "black",
			   label.r = unit(0, "lines"),
			   label.size = 0,
			   vjust = 0,
			   size = 3,
			   alpha = 1/2) +
	labs(x = "Condition",
		 y = "P(Target looking)",
		 colour = "Condition",
		 fill = "Condition") +
	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  strip.background = element_rect(fill = "grey90",
		  								colour = "grey90"),
		  panel.grid.major.y = element_line(linetype = "dotted",
		  								  colour = "grey")) 
```

#### Time course analysis

```{r fig-related}
#| label: fig-related
#| fig-height: 6
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *related* and *unrelated* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
plot_gamm <- function(data, model, contrast = "related") {

	epreds <- expand_grid(condition = levels(data$condition),
						  timebin = seq(0, 20, length.out = 100),
						  age = c(21, 25, 30),
						  lp = levels(data$lp),
						  .nsamples = 1) |> 
		add_epred_draws(model,
						ndraws = 100,
						re_formula = NA, 
						value = ".value") |> 
		mutate(lp = factor(lp, 
						   levels = c("Monolingual (English)",
						   		   "Monolingual",
						   		   "Bilingual")),
			   age = factor(age, levels = c(21, 25, 30),
			   			 labels = paste0(c(21, 25, 30), " months")))

	epreds_diff <- epreds |> 
		pivot_wider(names_from = condition,
					values_from = .value,
					id_cols = c(timebin, age, lp, .draw),
					names_repair = janitor::make_clean_names)

	if (contrast=="related") {
		epreds_diff$diff <- epreds_diff$related - epreds_diff$unrelated
	} else {
		epreds_diff$diff <- epreds_diff$cognate - epreds_diff$non_cognate
	}

	data |> 
		mutate(age = factor(age, levels = c(21, 25, 30),
							labels = paste0(c(21, 25, 30), " months"))) |> 
		summarise(.prop = mean(.prop),
				  .by = c(child_id, timebin, lp, condition, age))

	epreds |> 
		ggplot(aes(timebin, y = .value,
				   colour = condition,
				   fill = condition,
				   shape = condition,
				   linetype = condition)) +
		facet_grid(age~lp) +
		stat_summary(fun.data = \(x) mean_qi(x, .width = 0.95),
					 geom = "ribbon",
					 alpha = 0.5,
					 linewidth = 0) +
		stat_summary(aes(linetype = condition),
					 fun = "mean",
					 geom = "line",
					 linewidth = 3/4) +
		geom_hline(yintercept = 1/2, 
				   linewidth = 1/2,
				   colour = "black",
				   linetype = "dotted") +
		# stat_summary(fun.data = mean_se,
		# 			 geom = "errorbar",
		# 			 linetype = "solid",
		# 			 width = 0.25) +
		# stat_summary(fun = mean,
		# 			 geom = "point") +
		labs(x = "Time (ms)",
			 y = "P(Target looking)",
			 colour = "Condition",
			 fill = "Condition",
			 linetype = "Condition",
			 shape = "Condition") +
		theme(legend.title = element_blank(),
			  legend.position = "top",
			  axis.title.x = element_blank())

@@

### Cognate priming: Cognate vs. Non-cognate

```{r fig-cognate-aggregated}
#| label: fig-related-aggregated
#| fig-cap: "A) Aggregated probability of target looking for cognate and non-cognate trials. Each point represents the mean probability of target looking for one participant in one testing session. Lines link observations from the same testing session across conditions. Black dots and errorbars indicate the mean and 95% CrI. B) Aggregated probability of target looking across ages for cognate and non-cognate trials. Lines and error bands indicate the mean and standard error of the mean."
nd <- expand(data_cognate, lp, condition, age = mean(data_cognate$age))

epreds <- add_epred_draws(newdata = nd,
						  object = model_fits_cognate[[1]],
						  re_formula = NA) |> 
	mean_qi() |> 
	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))

epreds |> 
	ggplot(aes(condition, .epred, 
			   colour = condition,
			   fill = condition)) +
	facet_wrap(~lp) +
	# geom_line(data = data_cognate,
	# 		  aes(y = .elog,
	# 		  	group = session_id),
	# 		  colour = "grey",
	# 		  alpha = 1/4) +
	geom_dots(dat = data_cognate,
			  aes(y = .elog,
			  	side = ifelse(condition=="Cognate",
			  				  "left", 
			  				  "right")),
			  show.legend = FALSE) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	geom_line(aes(group = lp),
			  colour = "black",
			  linewidth = 3/4) +
	geom_errorbar(aes(ymin = .lower,
					  ymax = .upper),
				  width = 0.15,
				  linewidth = 3/4,
				  colour = "black") +
	geom_point(size = 2, colour = "black") +
	geom_label(aes(label = label,
				   y = -1.5),
			   fill = "white",
			   colour = "black",
			   label.r = unit(0, "lines"),
			   label.size = 0,
			   vjust = 0,
			   size = 3,
			   alpha = 1/2) +
	labs(x = "Condition",
		 y = "P(Target looking)",
		 colour = "Condition",
		 fill = "Condition") +
	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  strip.background = element_rect(fill = "grey90",
		  								colour = "grey90"),
		  panel.grid.major.y = element_line(linetype = "dotted",
		  								  colour = "grey")) 
```

#### Time course analysis

```{r fig-cognate}
#| label: fig-cognate
#| fig-height: 6
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *cognate* and *non-cognate* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
plot_gamm(data_time_cognate,
		  model_fits_cognate[[1]],
		  contrast = "cognate")
```

@@

```{r fig-validity-target}
get_data(gaze = gaze,
		 participants = participants,
		 stimuli = stimuli,
		 vocabulary = vocabulary,
		 attrition_trials = attrition_trials,
		 attrition_participants = attrition_participants,
		 time_subset = c(0, 2),
		 contrast = "related",
		 is_valid_vocab_all) |> 
	unnest_wider(is_valid_vocab_all) |>
	select(session_id, lp, .elog, target) |> 
	arrange(session_id, target) |> 
	summarise(.elog_mean = mean(.elog),
			  .elog_sd = sd(.elog),
			  n = n(),
			  .by = c(lp, target)) |> 
	mutate(target = ifelse(target, "Yes", "No"),
		   .elog_se = .elog_sd/sqrt(n),
		   .elog_lower = .elog_mean - .elog_se*1.96,
		   .elog_upper = .elog_mean + .elog_se*1.96,
	) |> 
	ggplot(aes(lp, .elog_mean, 
			   ymin = .elog_lower,
			   ymax = .elog_upper,
			   colour = target)) +
	facet_wrap(~lp, ncol = 1, scales = "free_x") +
	geom_errorbar(width = 0.2, linewidth = 3/4, 
				  position = position_dodge(width = 0.25)) +
	geom_point(size = 2,
			   position = position_dodge(width = 0.25)) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	labs(x = "Condition",
		 y = "P(Target looking)", 
		 colour = "Knows the target word") +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted")) +

	get_data_time(gaze = gaze,
				  participants = participants,
				  stimuli = stimuli,
				  vocabulary = vocabulary,
				  attrition_trials = attrition_trials,
				  attrition_participants = attrition_participants,
				  time_subset = c(0, 2),
				  contrast = "related",
				  is_valid_vocab_all) |> 
	unnest_wider(is_valid_vocab_all) |>
	select(session_id, age, lp, timebin, .elog, target) |> 
	arrange(session_id, target) |> 
	summarise(.elog_mean = mean(.elog),
			  .elog_sd = sd(.elog),
			  n = n(),
			  .by = c(timebin, lp, target)) |> 
	mutate(target = ifelse(target, "Yes", "No"),
		   .elog_se = .elog_sd/sqrt(n),
		   .elog_lower = .elog_mean - .elog_se*1.96,
		   .elog_upper = .elog_mean + .elog_se*1.96,
	) |> 
	ggplot(aes(timebin, .elog_mean,
			   ymin = .elog_lower,
			   ymax = .elog_upper,
			   colour = target,
			   fill = target)) +
	facet_wrap(~lp, ncol = 1, scales = "free_x") +
	geom_line(linewidth = 1/2) +
	geom_ribbon(alpha = 1/2,
				colour = NA) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	labs(x = "Condition",
		 y = "P(Target looking)", 
		 fill = "Knows the target word",
		 colour = "Knows the target word") +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"),
		  axis.title.y = element_blank(),
		  axis.line.x = element_line()) +

>>>>

Growing a mental lexicon is one of the main achievements in the developmental journey of infants. Being able to store lexical representations of familiar words allows infants to later recognise them in speech, and to retrieve their associated concepts. The first step towards spoken word-recognition is the acoustic-phonetic processing of the speech signal. This results in the activation of lexical representations whose associated phonological forms matches the acoustic signal to some extent. The activated word-forms then compete for selection: the lexical system uses the auditory input, together with top-down context provided by grammatical, supra-segmental, and semantic constraints, to select the candidate lexical representation with the best match. There is evidence that spoken word recognition occurs in a *cascaded* fashion. The activation and selection of candidate lexical representations overlap in time, relying on partial information that accumulates as the speech signal unfolds [@marslen1987functional; @marslen1978processing; @grosjean1980spoken]. This cascaded activation triggered by lexical access also results in the activation of the concepts associated to the accesses phonological forms. @allopenna1998tracking.

This is also the case in the developing lexicon. There is evidence that infants start forming their first lexical representations before their first year of life. Already at six months of age, infants show evidence of word recognition.  When presented with pairs of familiar objects and hearing the label of one of them, 6-months-old infants and older show a looking preference towards the named object [@bergelson20126; @bergelson2015early]. @chow2017spoken adapted the Visual World Paradigm from @huettig2007tug to explore 24- to 30-month-old toddlers' visual fixation patterns during a word recognition when presented with phonological and semantic distractors. In each trial, the authors presented participants with four semantically and phonologically pictures. Four seconds after pictures onset, a word-form was auditorily presented. The word did not refer to any of the pictures displayed on the screen, but was phonologically related to one of them (both labels shared phonological onset), and semantically related to another one of the pictures (both referents belonged to the same taxonomic category. For instance, participants might be presented with the pictures of a sandwich, a bus, a cat, and a dress. Then they would hear the carrier phrase "Look at the **bee**!". The authors registered participants fixations to the phonological and semantic distractors, and found evidence of a preference for the phonological distractor at earlier stages of the post-naming phase, and a preference for the semantic distractor at later stages of the trial. These results support a cascaded activation account of lexical access during the first stages of lexical development.

@@

Marian and Spivey (1999)
Costa et al. (2000)

@dijkstra2019multilink

@@

##  How does language co-activation shape lexical development?

@@

## The present study

The present study is aimed at investigating the developmental trajectories of word recognition in bilingualism, and how (if at all) language non-selectivity shapes them. Using an adaptation of [@mani2010infants], we presented 20- to 32-months-old toddlers with a cross-linguistic phonological priming paradigm. We manipulated both the phonological overlap between the prime word and target word, and the cognate status of the prime word, to test the hypothesis that bilingual toddlers implicitly name familiar pictures in both languages. If so, phonological priming effect should be larger when the prime label in  both languages shares phonological overlap with the target words (cognate condition), compared to when only the label of the prime in one language overlaps phonologically with the target (non-cognate condition). We also also included a control *Unrelated* condition in which regardless of the cognate status of the prime word, neither of the prime labels in any language overlapped phonologically with the target word.

@@

```{r fig-ptlt-descriptive}
#| label: fig-ptlt-descriptive
#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
data_time |> 
	summarise(.elog = mean(.elog),
			  .by = c(session_id, timebin, lp, condition)) |> 
	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
	facet_wrap(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 width = 0.5) +
	stat_summary(fun = mean,
				 geom = "line") +
	stat_summary(fun = mean,
				 geom = "point") +
	theme(axis.title.x = element_blank()) +

	data_time |> 
	summarise(.elog = mean(.elog),
			  .by = c(session_id, timebin, lp, condition)) |> 
	ggplot(aes(timebin, .elog, colour = condition, fill = condition)) +
	facet_wrap(~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = mean_se,
				 geom = "errorbar",
				 width = 0.5) +
	stat_summary(fun = mean,
				 geom = "line") +
	stat_summary(fun = mean,
				 geom = "point") +
	theme(strip.text = element_blank()) +

@@

## Aggregated analysis

@@

```{r fig-related-aggregated}
#| label: fig-related-aggregated
#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials. Each point represents the mean probability of target looking for one participant in one testing session. Lines link observations from the same testing session across conditions. Black dots and errorbars indicate the mean and 95% CrI. B) Aggregated probability of target looking across ages for related and unrelated trials. Lines and error bands indicate the mean and standard error of the mean."
nd <- expand(data_aggr, lp, condition, age = seq(20, 32, length.out = 100))

epreds <- add_epred_draws(newdata = nd,
						  object = model_fits_aggr$fit_aggr_4,
						  re_formula = NA) |> 
	mean_qi() |> 
	mutate(label = sprintf("%.2f\n[%.2f, %.2f]", .epred, .lower, .upper))

epreds |> 
	ggplot(aes(age, .epred, 
			   colour = condition,
			   fill = condition)) +
	facet_wrap(~lp) +
	# geom_line(data = data_related,
	# 		  aes(y = .elog,
	# 		  	group = session_id),
	# 		  colour = "grey",
	# 		  alpha = 1/4) +
	# geom_dots(dat = data_aggr,
	# 		  aes(y = .elog),
	# 		  side = "both",
	# 		  show.legend = FALSE) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	geom_ribbon(aes(ymin = .lower,
					ymax = .upper),
				alpha = 1/3,
				linewidth = NA) +
	geom_line(linewidth = 3/4) +
	geom_point(data = data_aggr,
			   aes(y = .elog),
			   alpha = 1/2) +
	# geom_label(aes(label = label,
	# 			   y = -1.5),
	# 		   fill = "white",
	# 		   colour = "black",
	# 		   label.r = unit(0, "lines"),
	# 		   label.size = 0,
	# 		   vjust = 0,
	# 		   size = 3,
	# 		   alpha = 1/2) +
	labs(x = "Condition",
		 y = "P(Target looking)",
		 colour = "Condition",
		 fill = "Condition") +
	scale_y_continuous(breaks = seq(-4, 4, 0.5)) +
	theme(legend.position = "none",
		  axis.title.x = element_blank(),
		  strip.background = element_rect(fill = "grey90",
		  								colour = "grey90"),
		  panel.grid.major.y = element_line(linetype = "dotted",
		  								  colour = "grey")) 
```

## Time course analysis

```{r fig-time}
#| label: fig-time
#| fig-height: 6
#| fig-width: 8
#| fig-cap: "Marginal posterior predictions of the GAMMs in Analysis 1. (A) Mean posterior probability of target looking across the time course of the trial. Black lines and intervals indicate the psoterior mean and 95% credible intervals. Points indicate the mean probability of target looking across participants. (B) Difference in posterior probability of target looking between *related* and *unrelated* trials. The yellow rectangle indicates, in both A and B, the range of time points in which the 95% credible interval of the differences excluded zero."
plot_gamm <- function(data, model, contrast = "related") {

	nd <- expand_grid(condition = levels(data$condition),
					  timebin = seq(0, 17, length.out = 100),
					  age = mean(data$age),
					  # sesion_id = first(data$session_id),
					  # age = c(21, 25, 30),
					  lp = levels(data$lp))

	epreds <- add_epred_draws(newdata = nd,
							  object = model,
							  # ndraws = NULL,
							  re_formula = NA,
							  value = ".value") |> 
		mutate(lp = factor(lp, 
						   levels = c("Monolingual (English)",
						   		   "Monolingual",
						   		   "Bilingual")),
			   age = factor(age, levels = c(21, 25, 30),
			   			 labels = paste0(c(21, 25, 30), " months")))

	epreds_diff <- epreds |> 
		pivot_wider(names_from = condition,
					values_from = .value,
					id_cols = c(timebin, age, lp, .draw),
					names_repair = janitor::make_clean_names) 
	# 
	# if (contrast=="related") {
	# 	epreds_diff$diff <- epreds_diff$related - epreds_diff$unrelated
	# } else {
	# 	epreds_diff$diff <- epreds_diff$cognate - epreds_diff$non_cognate
	# }

	obs <- data |> 
		mutate(age = factor(age, levels = c(21, 25, 30),
							labels = paste0(c(21, 25, 30), " months"))) |> 
		summarise(.elog = mean(.elog),
				  .by = c(session_id, timebin, lp, condition, age))

	epreds |> 
		ggplot(aes(timebin, y = .value,
				   colour = condition,
				   fill = condition,
				   shape = condition)) +
		facet_wrap(~lp) +
		# stat_summary(fun.data = mean_qi,
		# 			 geom = "ribbon",
		# 			 alpha = 0.5,
		# 			 linewidth = 0) +
		stat_summary(aes(linetype = condition),
					 fun = mean,
					 geom = "line",
					 linewidth = 3/4) +
		geom_hline(yintercept = 0, 
				   linewidth = 1/2,
				   colour = "black",
				   linetype = "dotted") +
		stat_summary(data = obs,
					 aes(y = .elog),
					 fun.data = "mean_se",
					 geom = "errorbar",
					 width = 1,
					 linewidth = 3/4,
					 position = position_dodge(width = 0.5)) +
		stat_summary(data = obs,
					 aes(y = .elog),
					 fun = "mean",
					 geom = "point",
					 size = 2,
					 position = position_dodge(width = 0.5)) +
		# stat_summary(fun.data = mean_se,
		# 			 geom = "errorbar",
		# 			 linetype = "solid",
		# 			 width = 0.25) +
		# stat_summary(fun = mean,
		# 			 geom = "point") +
		labs(x = "Time (ms)",
			 y = "P(Target looking)",
			 colour = "Condition",
			 fill = "Condition",
			 linetype = "Condition",
			 shape = "Condition") +
		theme(legend.title = element_blank(),
			  legend.position = "top",
			  axis.title.x = element_blank())

@@

@@

```{r fig-validity-target}
get_data(gaze = gaze,
		 participants = participants,
		 stimuli = stimuli,
		 vocabulary = vocabulary,
		 attrition_trials = attrition_trials,
		 attrition_participants = attrition_participants,
		 time_subset = c(0, 2),
		 contrast = "related",
		 is_valid_vocab_all,
		 clean = FALSE) |> 
	unnest_wider(is_valid_vocab_all) |>
	select(session_id, lp, .elog, target) |> 
	arrange(session_id, target) |> 
	summarise(.elog_mean = mean(.elog),
			  .elog_sd = sd(.elog),
			  n = n(),
			  .by = c(lp, target)) |> 
	mutate(target = ifelse(target, "Yes", "No"),
		   .elog_se = .elog_sd/sqrt(n),
		   .elog_lower = .elog_mean - .elog_se*1.96,
		   .elog_upper = .elog_mean + .elog_se*1.96,
	) |> 
	ggplot(aes(lp, .elog_mean, 
			   ymin = .elog_lower,
			   ymax = .elog_upper,
			   colour = target)) +
	facet_wrap(~lp, ncol = 1, scales = "free_x") +
	geom_errorbar(width = 0.2, linewidth = 3/4, 
				  position = position_dodge(width = 0.25)) +
	geom_point(size = 2,
			   position = position_dodge(width = 0.25)) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	labs(x = "Condition",
		 y = "P(Target looking)", 
		 colour = "Knows the target word") +
	theme(legend.position = "none",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted")) +

	get_data_time(gaze = gaze,
				  participants = participants,
				  stimuli = stimuli,
				  vocabulary = vocabulary,
				  attrition_trials = attrition_trials,
				  attrition_participants = attrition_participants,
				  time_subset = c(0, 2),
				  contrast = "related",
				  is_valid_vocab_all,
				  clean = FALSE) |> 
	unnest_wider(is_valid_vocab_all) |>
	select(session_id, age, lp, timebin, .elog, target) |> 
	arrange(session_id, target) |> 
	summarise(.elog_mean = mean(.elog),
			  .elog_sd = sd(.elog),
			  n = n(),
			  .by = c(timebin, lp, target)) |> 
	mutate(target = ifelse(target, "Yes", "No"),
		   .elog_se = .elog_sd/sqrt(n),
		   .elog_lower = .elog_mean - .elog_se*1.96,
		   .elog_upper = .elog_mean + .elog_se*1.96,
	) |> 
	ggplot(aes(timebin, .elog_mean,
			   ymin = .elog_lower,
			   ymax = .elog_upper,
			   colour = target,
			   fill = target)) +
	facet_wrap(~lp, ncol = 1, scales = "free_x") +
	geom_line(linewidth = 1/2) +
	geom_ribbon(alpha = 1/2,
				colour = NA) +
	geom_point(size = 2) +
	geom_hline(yintercept = 0,
			   linetype = "dashed") +
	labs(x = "Condition",
		 y = "P(Target looking)", 
		 fill = "Knows the target word",
		 colour = "Knows the target word") +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"),
		  axis.title.y = element_blank(),
		  axis.line.x = element_line()) +
